True versus apparent shapes of astrophysical bow shocks

### 2017-02-23 papers/Paper1/sec-thin-shell.tex
Add the new figures to the thin shell section (sec 5)

>>>>

\subsection{Projection effects in the thin shell model}
\label{sec:proj-effects-thin}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/two-quadric-R90-vs-Rc}
  \caption{Diagnostic diagram for thin shell models}
  \label{fig:thin-shell-R90-Rc}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/two-quadric-R90-Rc-snapshots}
  \caption{Variation with inclination angle of radii diagnostics}
  \label{fig:thin-shell-R90-Rc-snapshots}
\end{figure*}
